% !TEX program = LuaLaTeX
%-------------------------
% Author: Byung Moon Kim
% Website: kimbm2014@gmail.com
% License: Creative Commons CC BY 4.0
%-------------------------

\documentclass[10pt]{article}
\usepackage[a4paper, left=0.75in, right=0.75in, top=1in, bottom=1in]{geometry}
\usepackage[english]{babel}
\usepackage[OT1]{fontenc}
\usepackage{setspace}
\usepackage{emoji}
\usepackage{resume}
\usepackage{fontspec}

\hyphenation{Some-long-word}
\setmainfont{Helvetica Neue}
\setstretch{1.15}

\begin{document}

\begin{flushright}
	Byung Moon Kim \\
	\href{mailto:kimbm2014@gmail.com}{kimbm2014@gmail.com} \\
	Mountain View, CA \\
	213.407.1213 \\
	\raisebox{-0.5ex}{\emoji{handshake}}\hspace{0.1ex} \href{https://www.linkedin.com/in/ray-kim0727/}{LinkedIn}\hspace{1.0ex}
	\raisebox{-0.5ex}{\emoji{blue-book}}\hspace{0.1ex} \href{https://github.com/moonnada}{Github}\hspace{1.0ex}
	\raisebox{-0.5ex}{\emoji{globe-showing-americas}}\hspace{0.1ex} \href{https://raykim0727.vercel.app/}{Portfolio}\hspace{1.0ex}
\end{flushright}

\vspace{1cm}

\noindent 06/06/2024

\vspace{1cm}

\noindent Dear Cloudflare Hiring Team,

\vspace{0.5cm}

I am writing to express my interest in the Frontend Software Engineer - Network Services at Cloudflare.\\ I have developed robust web applications and am eager to contribute to your team’s success. My background in software development and my passion for innovative solutions make me a great fit for this role.
\vspace{0.5cm}

Throughout my career, I have honed my skills in various programming languages and frameworks. Specifically, I am proficient in:

\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages}: TypeScript, JavaScript, Python
    \item \textbf{Frameworks and Technologies}: HTML5, SASS, React, Redux, Cypress, Playwright, GraphQL, Apollo Client Query, REST APIs
\end{itemize}

In my recent role at CrowdDoing as a Software Engineer, I created reusable React components, reducing code duplication, and implemented AI-driven features to enhance development efficiency. My work at Genemod involved developing web applications with React, TypeScript, and Redux, significantly improving user engagement and page load speed, and refactoring a legacy codebase to TypeScript. At Underwatch, I increased user interaction through redesigns and improved data accuracy using GraphQL. During my IBM apprenticeship, I led a team, managed projects, and implemented CI/CD strategies. Additionally, my internship at StemAway involved configuring and building themes and plugins for Discourse using JavaScript and DOM structure.
\vspace{0.5cm}

One of my key strengths is my expertise in E2E testing. At Genemod, I utilized Cypress and Playwright to implement comprehensive testing strategies, ensuring the reliability and performance of our applications. This experience has made me adept at identifying and resolving issues before they impact users.
\vspace{0.5cm}

I hold a B.S. in Software Engineering from San Jose State University, with relevant coursework in Computer Architecture, Computer Network, Object-Oriented Design, Software Engineering, Operating Systems, Software Quality Testing, and Database Management.
\vspace{0.5cm}

I am excited about the possibility of contributing to Cloudflare and am confident that my background, skills, and enthusiasm for innovative software development will be a valuable asset to your team. Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to your team.
\vspace{0.5cm}

\noindent Sincerely, \\
\noindent Byung Moon Kim

\end{document}
