\documentclass[a4paper,10pt]{article}
\usepackage{newtxtext}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

\geometry{left=0.5in, right=0.5in, top=0.3in, bottom=0.3in}

\setlist[itemize]{left=0pt}

% Formatting sections
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

% Remove the box around hyperlinks and change the link color to black
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black
}

% Reduce space before and after sections
\titlespacing*{\section}
{0pt}{1ex plus 0.5ex minus .2ex}{0.5ex plus .2ex}

% Reduce space between items in itemize
\setlist{nosep}

% Reduce overall document font size slightly
\renewcommand{\normalsize}{\fontsize{11.5}{12.5}\selectfont}

\begin{document}
\pagestyle{empty}

% Header
\begin{center}
    {\LARGE \textbf{Byung Moon Kim}}
\end{center}
\noindent \begin{center}
    kimbm2014@gmail.com \,|\, Mountain View, CA \,|\, 213.407.1213 \,|\, \href{https://www.linkedin.com/in/ray-kim0727}{LinkedIn} \,|\, \href{https://github.com/moonnada}{Github} \,|\, \href{https://raykim0727.vercel.app/}{Portfolio}
\end{center}

\vspace{1.5mm}

% Centered summary
\begin{center}
    Experienced Frontend Engineer with a track record of developing robust web applications.\\
    Seeking a full-time position in a dynamic organization where I can contribute to the team’s success.
\end{center}

\vspace{1.5mm}

\section*{Skills}\vspace{0.5mm}
\begin{itemize}
    \item \textbf{Programming Languages}: TypeScript, JavaScript, Python\vspace{0.5ex}
    \item \textbf{Frameworks and Technologies}: HTML5, SASS, React, Redux, GraphQL, Apollo Client, REST APIs\vspace{0.5ex}
    \item \textbf{Testing and CI/CD}: React Testing Library, Playwright, Cypress, GitHub Actions, Gitlab\vspace{0.5ex}
    
\end{itemize}

\vspace{3mm}

\section*{Work Experience}\vspace{0.5mm}
\noindent \textbf{CrowdDoing} \hfill {San Jose}\\
\vspace{0.5mm}
\textit{Frontend Engineer} \hfill {January 2024 - Present}\vspace{-\baselineskip}
\vspace{2.5mm}
\begin{itemize}
    \item Spearheaded the development of reusable \textbf{React} components, enhancing development efficiency.\vspace{0.3ex}
    \item Engineered responsive and accessible user interfaces, optimizing user experience across different devices.\vspace{0.3ex}
    \item Conducted comprehensive unit testing using \textbf{React Testing Library}, ensuring high-quality, defect-free code.\vspace{0.3ex}
    \item Coordinated with UI/UX teams using JIRA for aligning priorities through design reviews and issue tracking.\vspace{0.3ex}
\end{itemize}

\vspace{3mm}

\noindent \textbf{Genemod} \hfill {San Jose}\\
\textit{Frontend Engineer} \hfill {June 2022 - May 2023}\vspace{-\baselineskip}
\vspace{2.5mm}
\begin{itemize}
    \item Developed and executed advanced web applications using \textbf{React, TypeScript, and Redux}, leading to improved user engagement and page load speed.\vspace{0.3ex}
    \item Refactored a legacy JavaScript codebase to TypeScript, implementing type safety and improving code maintainability.\vspace{0.3ex}
    \item Integrated \textbf{RESTful APIs} with frontend applications, leveraging Django to ensure seamless data exchange and optimal application performance.\vspace{0.3ex}
    \item Implemented E2E testing strategies with \textbf{Cypress and Playwright}, enhancing application reliability.\vspace{0.3ex}
\end{itemize}

\vspace{3mm}

\noindent \textbf{Underwatch} \hfill {San Jose}\\
\textit{Frontend Engineer} \hfill {October 2021 - May 2022}\vspace{-\baselineskip}
\vspace{2.5mm}
\begin{itemize}
    \item Boosted user interaction through the implementation of redesigned main and statistics pages using React, providing a more intuitive user experience.\vspace{0.3ex}
    \item Aggregated and systematized user information by integrating Instagram and Facebook APIs with \textbf{GraphQL}, increasing data accuracy and streamlining data retrieval processes.\vspace{0.3ex}
    \item Collaborated with the QA team to identify and resolve bugs, ensuring a stable and reliable product release.\vspace{0.3ex}
\end{itemize}

\vspace{3mm}

\noindent \textbf{IBM} \hfill {Los Angeles}\\
\textit{Frontend Engineer Apprentice} \hfill {June 2021 - August 2021}\vspace{-\baselineskip}
\vspace{2.5mm}
\begin{itemize}
    \item Led a team in developing a modern frontend application using \textbf{React and Redux}, focusing on delivering a seamless user experience.\vspace{0.3ex}
    \item Managed project development and documentation via GitHub, implementing CI/CD strategies to streamline deployment processes.\vspace{0.3ex}
    \item Demonstrated strong collaboration and communication skills, effectively working with designers and backend developers.\vspace{0.3ex}
\end{itemize}

\vspace{3mm}

\noindent \textbf{StemAway} \hfill {Los Angeles}\\
\textit{Frontend Engineer Intern} \hfill {June 2021 - August 2021}\vspace{-\baselineskip}
\vspace{2.5mm}
\begin{itemize}
    \item Configured and built a theme and plugin for an open-source community forum software, Discourse, enhancing user interaction and engagement.\vspace{0.3ex}
    \item Utilized Object Oriented Programming in \textbf{JavaScript} and DOM structure to implement various frontend functionalities, improving the forum’s usability and performance.\vspace{0.3ex}
\end{itemize}

\vspace{3mm}

\section*{Education}\vspace{0.5mm}
\noindent \textbf{San Jose State University | Charles W. Davidson College of Engineering} \hfill \textit{B.S. Software Engineering} \hfill 
\begin{itemize}
    \item Relevant Coursework: Computer Architecture, Probability \& Statistics in Engineering, Computer Network,\\Object Oriented Design, Software Engineering I, II, Operating Systems, Software Quality Testing, Database
\end{itemize}
\end{document}
